Forecasting the Toronto Shelter System Performance on Reducing Chronic Homelessness 

### 2024-11-27 paper/paper.qmd
updated paper.qmd and rendered as paper.pdf

---
title: "Forecasting the Toronto Shelter System Performance on Reducing Chronic Homelessness "
subtitle: "My subtitle if needed"
author: 
  - Sarah Ding
thanks: "Code and data are available at: [https://github.com/sarahdingg/Toronto_Shelter_System_Forecast)."
date: today
date-format: long
abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
format: pdf
number-sections: true
bibliography: references.bib
---

@@

```{r}
#| echo: false
#| eval: true
#| warning: false
#| message: false
#| label: fig-interaction
#| fig-cap:

@@

# Summarize the average interaction terms per year
interaction_summary <- filtered_data %>%
  group_by(year) %>%
  summarise(
    avg_under16 = mean(interaction_age_under16_time, na.rm = TRUE),
    avg_16_24 = mean(interaction_age16_24_time, na.rm = TRUE),
    avg_25_34 = mean(interaction_age25_34_time, na.rm = TRUE),
    avg_35_44 = mean(interaction_age35_44_time, na.rm = TRUE),
    avg_45_54 = mean(interaction_age45_54_time, na.rm = TRUE),
    avg_55_64 = mean(interaction_age55_64_time, na.rm = TRUE),
    avg_65over = mean(interaction_age65over_time, na.rm = TRUE)
  ) %>%
  pivot_longer(
    cols = starts_with("avg"),
    names_to = "age_group",
    values_to = "average_value"
  ) %>%
  mutate(age_group = recode(age_group,
                            avg_under16 = "Under 16",
                            avg_16_24 = "16-24",
                            avg_25_34 = "25-34",
                            avg_35_44 = "35-44",
                            avg_45_54 = "45-54",
                            avg_55_64 = "55-64",
                            avg_65over = "65+"))

# Create the line plot
ggplot(interaction_summary, aes(x = year, y = average_value, color = age_group, group = age_group)) +
  geom_line(size = 1) +                 # Add trend lines
  geom_point(size = 2, alpha = 0.7) +   # Add data points
  labs(
    title = "Average Interaction Terms for Age Groups Over Time (2019-2023)",
    x = "Year",
    y = "Average Interaction Term Value",
    color = "Age Group"
  ) +
  theme_minimal() +
  theme(
    legend.position = "right",
    plot.title = element_text(hjust = 0.5)
  )

@@

Please don't use these as sub-heading labels - change them to be what your point actually is.

>>>>

---
title: "Forecasting the Toronto Shelter System Performance on Reducing Chronic Homelessness "
subtitle: ""
author: 
  - Sarah Ding
thanks: "Code and data are available at: [https://github.com/sarahdingg/Toronto_Shelter_System_Forecast)."
date: today
date-format: long
abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
format: pdf
number-sections: true
bibliography: references.bib
---

@@

```{r}
#| echo: false
#| eval: true
#| warning: false
#| message: false
#| label: fig-interaction
#| fig-cap: Trends in Average Interaction Terms for Age Groups Over Time (2018–2023)

@@

# Summarize the average interaction terms per year
interaction_summary <- filtered_data %>%
  group_by(year) %>%
  summarise(
    avg_under16 = mean(interaction_age_under16_time, na.rm = TRUE),
    avg_16_24 = mean(interaction_age16_24_time, na.rm = TRUE),
    avg_25_34 = mean(interaction_age25_34_time, na.rm = TRUE),
    avg_35_44 = mean(interaction_age35_44_time, na.rm = TRUE),
    avg_45_54 = mean(interaction_age45_54_time, na.rm = TRUE),
    avg_55_64 = mean(interaction_age55_64_time, na.rm = TRUE),
    avg_65over = mean(interaction_age65over_time, na.rm = TRUE)
  ) %>%
  pivot_longer(
    cols = starts_with("avg"),
    names_to = "age_group",
    values_to = "average_value"
  ) %>%
  mutate(age_group = recode(age_group,
                            avg_under16 = "Under 16",
                            avg_16_24 = "16-24",
                            avg_25_34 = "25-34",
                            avg_35_44 = "35-44",
                            avg_45_54 = "45-54",
                            avg_55_64 = "55-64",
                            avg_65over = "65+"),
         age_group = factor(age_group, levels = c("Under 16", "16-24", "25-34", "35-44", "45-54", "55-64", "65+")))

# Create the plot with smoother curves and reordered legend
ggplot(interaction_summary, aes(x = year, y = average_value, color = age_group, group = age_group)) +
  geom_smooth(se = FALSE, method = "loess", size = 1) +  # Add smooth curves
  geom_point(size = 2, alpha = 0.7) +
  labs(
    title = "Average Interaction Terms for Age Groups Over Time (2018-2023)",
    x = "Year",
    y = "Average Interaction Term Value",
    color = "Age Group"
  ) +
  theme_minimal() +
  theme(
    legend.position = "right",
    plot.title = element_text(hjust = 0.5)
  ) +
  scale_y_continuous(expand = c(0, 0), limits = c(-0.5, 1)) +  # Allow for negative values
  scale_color_manual(
    values = c("pink", "red", "orange", "green", "blue", "purple", "brown")  # Custom colors
  )

@@

Which age groups benefit most over time from system improvements.
Age groups that require more attention if their outcomes worsen over time.
Policy implications, such as whether programs targeted at specific age groups need to be adjusted to meet changing needs.
